\hspace{1cm} Do syntactic and semantic similarity lead to interference effects?\newline Evidence from self-paced reading and event-related potentials using German

### 2023-10-17 paper/main.tex
fixed bib

An obvious difference from previous studies is the experimental methodology. The majority of the previous experiments employed eye-tracking while reading, while we used a self-paced reading task. Self-paced reading (SPR) could trigger a greater tendency to cause interference effects compared to natural reading (as in eye-tracking studies), due to the restricted reading format in SPR: Comprehenders have no opportunity to revisit previous material during conventional self-paced reading \citep[but see][]{BSPR}. SPR is likely to be more demanding on the comprehender's memory, which might make it easier to detect interference effects. This argumentation is supported by our estimation of the results of \citeauthor{vandyke07}'s (\citeyear{vandyke07}) Experiment 1, the only other self-paced reading experiment using this design (see Figure \ref{fig:previous} in the appendix):  In the critical region, the estimates of both main effects (syntactic and semantic interference) are very similar to the results of the present study; the interaction effect observed by \citeauthor{vandyke07} in the spill-over region is also similar to our estimate. However, it remains unclear why semantic interference was especially prominent in our study compared to the previous ones.

>>>>

An obvious difference from previous studies is the experimental methodology. The majority of the previous experiments employed eye-tracking while reading, while we used a self-paced reading task. Self-paced reading (SPR) could trigger a greater tendency to cause interference effects compared to natural reading (as in eye-tracking studies), due to the restricted reading format in SPR: Comprehenders have no opportunity to revisit previous material during conventional self-paced reading \citep[but see][]{BSPR}. SPR is likely to be more demanding on the comprehender's memory, which might make it easier to detect interference effects. This argumentation is supported by our estimation of the results of \citeauthor{vandyke07}'s (\citeyear{vandyke07}) Experiment 1, the only other self-paced reading experiment using this design: %(see Figure \ref{fig:previous} in the appendix):
In the critical region, the estimates of both main effects (syntactic and semantic interference) are very similar to the results of the present study; the interaction effect observed by \citeauthor{vandyke07} in the spill-over region is also similar to our estimate. However, it remains unclear why semantic interference was especially prominent in our study compared to the previous ones.
